Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Revert "Simplify language in the "older-Rahel" story."
This reverts commit b63497cd0917142a8afc8cf0bdbc20cf7eee4460.

I was trying to distinguish between writing stories (which even younger
Rahel was doing) and writing code (which is what older Rahel is learning
to do).  This paragraph could be clarified, but not in the direction of
the reverted commit.

An older Rahel learns that the block language she used to talk with
the turtle is also used to write all the software and stories running inside
her special book.  Rahel begins to write new stories with her own
music and dialog, which make the green book even more
exciting for her younger brother and the other younger kids just now
receiving them.

>>>>

An older Rahel learns that the block language she used to talk with
the turtle is also used to write all the software running inside
her special book.  Rahel begins to write stories with different
kinds of new music functionality, which make the green book even more
exciting for her younger brother and the other younger kids just now
receiving them.
